Rapid Cycleway Prioritisation Tool

### 2020-06-11 code/index.Rmd
cohesive network text

This layer represents what a joined-up cycle network could look like if new cycleways were placed along corridors of high potential, by either closing roads to motorised traffic or creating one-way systems.
It shows what a joined-up cycle network could look like if there were no constraints on road space, along some of the most important corridors.

The cohesive network layer supports consideration of **long term** plans and alternatives to road space reallocation.
Road sections in the cohesive network but not in the Top ranked new cycleway layer may be suitable candidates for one way streets, where there may be insufficient space for road space reallocation without changing the navigable network for motor traffic.
The cohesive network layer was created to highlight the need for cohesive cycle network that and do not 'give up' at awkward junctions.
Cohesive networks are a key to getting people cycling [@buehler_bikeway_2016].

The layer was generated by first identifying the roads (classified by reference number) on which there is most cycling potential across the city and joining them together.
Specifically we first selected all road segments with cycle potential in the 85th percentile and above, which also belong to classified trunk roads, A roads or B roads.
These segments are then joined together to form a continuous network.

>>>>

This layer represents what a joined-up cycle network could look like if new cycleways were placed along the key corridors of high potential. 
Unlike the 'top ranked new cycleways' layer, the cohesive network comprises all of the major high cycle potential corridors, including sections where the roads are narrower. 
It shows what a joined-up cycle network could look like if there were no constraints on road space, along some of the most important corridors.

The cohesive network layer includes sections where there may be insufficient space for road space reallocation without changing the navigable network for motor traffic.
It was created to highlight the need for a cohesive cycle network that does not 'give up' at awkward junctions.
Cohesive networks are a key to getting people cycling [@buehler_bikeway_2016].

This layer supports consideration of **long term** plans and alternatives to road space reallocation.
Some sections of the cohesive network may still be suitable candidates for road-space reallocation (for example, [in Lancaster](https://www.facebook.com/photo.php?fbid=10158393513440797&set=gm.1409892779205719&type=1&theater) protected cycle lanes have recently been installed on a road which is less than 10 m in width), but other sections may be best suited to different types of traffic measure, such as point closures, cycleway installation on a nearby parallel alignment, or conversion to one way streets in order to free up space for cycle lanes.

The layer was generated by identifying the roads (classified by reference number) on which there is greatest cycling potential across the region and joining them together.
Specifically we first selected all road segments with cycle potential in the 85th percentile and above, which also belong to classified trunk roads, A roads or B roads.
These segments are then joined together to form a continuous network.
